### 2020-03-24 korea.tex
updates

While we find clear, positive correlations between the normalized traffic and the median estimates of $\mathcal R_t$ in both Daegu ($r=0.90$; 95\% CI: 0.79--0.95) and Seoul ($r=0.76$; 95\% CI: 0.57--0.87), these correlations are conflated by time trends, and are also likely conflated by other measures that could have affected $\mathcal R_t$ --
in particular, the increase in the number of tests as well as the improvement in the accuracy of case identification (Supplementary Materials).
We do not find clear signatures of lagged correlation between $\mathcal R_t$ and traffic volume (Supplementary Materials).
Similar patterns in the estimates of $\mathcal R_t$ are found in directly surrounding provinces (Gyeongsangbuk-do and Gyeonggi-do), providing support for the robustness of our analysis (Supplementary Materials).

>>>>

While we find clear, positive correlations between the normalized traffic and the median estimates of $\mathcal R_t$ in both Daegu ($r=0.90$; 95\% CI: 0.79--0.95) and Seoul ($r=0.76$; 95\% CI: 0.59--0.87), these correlations are conflated by time trends, and are also likely conflated by other measures that could have affected $\mathcal R_t$ --
in particular, the increase in the number of tests as well as the improvement in the accuracy of case identification (Supplementary Materials).
We do not find clear signatures of lagged correlation between $\mathcal R_t$ and traffic volume (Supplementary Materials).
Similar patterns in the estimates of $\mathcal R_t$ are found in directly surrounding provinces (Gyeongsangbuk-do and Gyeonggi-do), providing support for the robustness of our analysis (Supplementary Materials).

### 2020-03-24 supp.tex
updates

Testing criteria expanded 4 times between January 20--March 16, 2020: January 28, February 7, February 20, and March 2, 2020.
We accounted for these changes by assuming that the proportion positive should remain roughly constant if we follow a consistent protocol of identifying and deciding whom to test.
To do so, we calculated the relative proportion of positive cases during each period (divided by the the between-period mean) and multiplied the daily number of reported cases by the relative proportions of the corresponding criterion.
A sensitivity analysis showed that results are robust to these adjustments.

We then estimated time-dependent \emph{backward} onset-to-confirmation delay distributions from the partial line list. We asked: Given a cohort of individuals who were reported on the same day, what is the probability distribution of the onset-to-confirmation delay?
The backward delay distribution depends on changes in the number of symptomatic cases ---
e.g., when the number of symptomatic cases are increasing, the backward delay distribution is likely to be shorter because individuals are more likely to have developed symptoms recently.
The backward delay distribution was inferred using a negative-binomial regression with log-link using the \texttt{brms} package \citep{burkner2017brms}.
Time-dependent mean of the negative binomial distribution is modeled using splines.
We assumed weakly informative priors on the fixed effects: normal distributions with mean of 0 and standard deviation of 2;
these distributions are priors on link scale.

@@

To account for right-censoring in the reported cases, we also estimated time-dependent \emph{forward} onset-to-confirmation delay distribution using the same negative-binomial regression model.
Here, we asked: Given a cohort of individuals who became symptomatic on the same day, what is the probability distribution of the onset-to-confirmation delay?
The forward delay distribution reflects the changes in the accuracy of case identification --- e.g., a decrease in the delay reflects improvement in accuracy.

@@

For each combination of date of infection and a posterior sample of the forward delay distribution, we drew 1000 samples of incubation periods and onset-to-confirmation delays and calculated the median probability that an individual infected on a given day will be confirmed before March 16, 2020.
We divided the daily number of

We combined the forward delay distribution with the , we calculated the median probability that a

to calculate the median probability that a case infected on a given day will be reported before March 16, 2020.
Changes in the mean backward delay (\fref{dist}C) reflect changes in incidence of symptomatic cases, whereas the decrease in the mean forward delay (\fref{dist}D) reflects the improvement in the accuracy of case identification \citep{lai2020effect}.

>>>>

Testing criteria expanded 4 times between January 20--March 16, 2020: January 28, February 7, February 20, and March 2, 2020.
We accounted for these changes by assuming that the proportion positive should remain roughly constant if we follow a consistent protocol of identifying and deciding whom to test.
To do so, we calculated the relative proportion of positive cases during each period (divided by the the between-period mean) and multiplied the daily number of reported cases by the relative proportions of the corresponding criterion.
Sensitivity analyses showed that results are robust to these adjustments.

We then estimated time-dependent \emph{backward} onset-to-confirmation delay distributions from the partial line list: Given a cohort of individuals who were reported on the same day, what is the probability distribution of the onset-to-confirmation delay?
The backward delay distribution depends on changes in the number of symptomatic cases ---
e.g., when the number of symptomatic cases are increasing, the backward delay distribution is likely to be shorter because individuals are more likely to have developed symptoms recently.
The backward delay distribution was inferred using a negative-binomial regression with log-link using the \texttt{brms} package \citep{burkner2017brms}.
Time-dependent mean of the negative binomial distribution is modeled using splines.
We assumed weakly informative priors on the fixed effects: normal distributions with mean of 0 and standard deviation of 2;
these distributions are priors on link scale.

@@

To account for right-censoring in the reported cases, we also estimated time-dependent \emph{forward} onset-to-confirmation delay distribution using the same negative-binomial regression model: Given a cohort of individuals who became symptomatic on the same day, what is the probability distribution of the onset-to-confirmation delay?
The forward delay distribution reflects the changes in the accuracy of case identification --- e.g., a decrease in the delay reflects improvement in accuracy.

@@

For each combination of date of infection and a posterior sample of the forward delay distribution, we drew 1000 samples of incubation periods and onset-to-confirmation delays and calculated the median probability that an individual infected on a given day will be confirmed before March 16, 2020.
Finally, we divided the daily number of infected cases by the median probability that an infected case on a given day will be confirmed before Marh 16, 2020.
